%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author:
% Puneet Saini
%
% Repository:
% https://github.com/puneet29/puneet-resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{puneet-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Puneet Saini}\\
\end{large}
Systems Engineer\\
(Data Engineer)\\
Tata Consultancy Services Ltd.\\
Bengaluru
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

Github:// \href{https://github.com/puneet29}{\custombold{puneet29}} \\
LinkedIn://  \href{https://www.linkedin.com/in/geekpuneet}{\custombold{geekpuneet}} \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{Programming}
Python, Scala
\vspace{6pt}
\subsection{Frameworks|Tools|Libraries}
Spark, Hive, Pytorch, Numpy, FBProphet,\\
Pandas, Matplotlib, Plotly, OpenCV,\\
Seaborn, Spark, Hive, AWS EC2, AWS S3
\vspace{6pt}
\subsection{Databases}
Oracle SQL, MySQL
\vspace{6pt}
\subsection{Web Technologies}
Flask, HTML, CSS, JS
\vspace{6pt}
\subsection{Others}
Markdown, Git, Vim, PuTTY,\\
IntelliJ Idea, Notepad++, Jira,\\
Confluence, Jupyter Notebook,\\
Adobe Illustrator, Photoshop
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Data Structures\\
Algorithm\\
Neural Networks\\
Discrete Mathematics\\
Operating Systems\\
MySQL\\
Data Analysis
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2016-2020}
\subsection{B.Tech. CSE}
Guru Nanak Dev University, Amritsar\\
CGPA : 8.73/10\\
\vspace{8pt}
\datecolor{2015-2016}
\subsection{Intermediate}
Bhavan's SL Public School, Amritsar\\
Percentage: 91.8\%\\
\vspace{8pt}
\datecolor{2013-2014}
\subsection{High School}
Bhavan's SL Public School, Amritsar\\
GPA: 9/10
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill H 4/1199, Gali no. 1, Judge Nagar \\
\hspace*{0pt}\hfill Amritsar, Punjab-143001, India \\
\hspace*{0pt}\hfill Mob.: +91-9888096255 \\
\hspace*{0pt}\hfill Email:\textbf{\href{mailto:puneet29saini@gmail.com}{puneet29saini@gmail.com}} \\
\hspace*{0pt}\hfill Web:\textbf{\href{http://puneet29.github.io}{http://puneet29.github.io}} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2020-now} \runsubsection{TCS, Bengaluru}
\descript{Systems Engineer}
\noindent
\hspace{5em}%
\begin{tightemize}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
	\item Developing data pipelines in Spark Scala.
	\item Automating the testing process to increase efficiency by almost 80\%.
	\item Analysis of data to create dimension and fact tables.
	\item Creating shell scripts to automate recurring jobs.
\end{minipage}
\end{tightemize}
\descriptright{Scala, Spark, Hive, Oracle SQL, Jira, Unix}
\sectionsep

\datecolor{2020-2020} \runsubsection{Stylumia}
\descript{Product Engineering Intern}
\noindent
\hspace{5em}%
\begin{tightemize}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
	\item Performing Exploratory Data Analysis.
	\item Developed a high level data visualization library to improve efficiency by 60\%.
	\item Predicting sales and adequate inventory flow.
	\item Building and optimizing machine learning models.
\end{minipage}
\end{tightemize}
\descriptright{Python, Pandas, Numpy, Scikit, Pytorch, Plotly, Jupyter, FBProphet}
\sectionsep

\datecolor{2018-2018} \runsubsection{Redinmex, Mexico - Remote}
\descript{Freelancer}
\noindent
\hspace{5em}%
\begin{tightemize}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
	\item Gathering appropriate dataset to work on.
	\item Creating visualizations for end-user.
\end{minipage}
\end{tightemize}
\descriptright{Python, OpenCV, Jupyter, VastAI, Pytorch, Numpy, Pandas}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements/Awards} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{20XX-now} \runsubsection{Competition}
\descript{Status}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Description
\end{minipage}
\datecolor{20XX-now} \runsubsection{Competition}
\descript{Status}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Description
\end{minipage}
\datecolor{20XX-now} \runsubsection{Competition}
\descript{Status}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Description
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Side Projects}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2020-2020} \runsubsection{Tic Tac Toe RL}
\descript{Python, Numpy, Pygame}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Tic Tac Toe reinforcement learning model using Deep Q Learning.
Also included the minmax model to train Q learning model.
Made the GUI in Pygame.
\end{minipage}
\datecolor{2019-2019} \runsubsection{Fast Artistic Style Transfer}
\descript{Pytorch, Flask, AWS S3, AWS EC2}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
A web app made using flask which uses pretrained models to stylize your image
with selected style image. Implemented using Johnson et al. paper.
\end{minipage}
\datecolor{2019-2019} \runsubsection{Intel Scene Classification}
\descript{Pytorch, Jupyter, Flask}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Scene Classification model for Analytics Vidhya's Competition.\\
Hosted the app on Heroku.
\end{minipage}
\datecolor{2019-2019} \runsubsection{Skin Cancer Classification}
\descript{Pytorch, Jupyter}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{5pt}}
Skin cancer classification model which classifies three types of skin cancers.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}