%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author:
% Puneet Saini
%
% Repository:
% https://github.com/puneet29/puneet-resume
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{puneet-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Puneet Saini}\\
\end{large}
Software Engineer\\
(Data Engineer)\\
Bengaluru
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{Programming}
Python, Scala
\vspace{6pt}
\subsection{Frameworks|Tools|Libraries}
Spark, Hive, Pytorch, Numpy, FBProphet,\\
Pandas, Matplotlib, Plotly, OpenCV,\\
Seaborn, AWS EC2, AWS S3
\vspace{6pt}
\subsection{Databases}
Oracle SQL, MySQL
\vspace{6pt}
\subsection{Web Technologies}
Flask, HTML, CSS, JS
\vspace{6pt}
\subsection{Others}
Markdown, Git, Vim, PuTTY,\\
Jira, Confluence,\\
Adobe Illustrator, Photoshop
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2016-2020}
\subsection{B.Tech. CSE}
Guru Nanak Dev University, Amritsar\\
CGPA : 8.73/10\\
\vspace{8pt}
\datecolor{2015-2016}
\subsection{Intermediate}
Bhavan's SL Public School, Amritsar\\
Percentage: 91.8\%\\
\vspace{8pt}
\datecolor{2013-2014}
\subsection{High School}
Bhavan's SL Public School, Amritsar\\
GPA: 9/10
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     VOLUNTEER WORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Volunteer Work} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2018-2019}
\subsection{Chief Organizer}
Hack Zero To One\\
\vspace{8pt}
\datecolor{2018-2019}
\subsection{Technical Head}
CESS, GNDU\\
\vspace{8pt}
\datecolor{2017-2018}
\subsection{Design Head}
CESS, GNDU\\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS/COURSES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications/Courses}
\noindent\rule{5cm}{0.4pt}

SAFe 5 Practitioner\\
Neural Networks and Deep Learning\\
Convolutional Neural Networks\\
Apache Spark with Scala\\
Data visualization: Storytelling\\
Pytorch Scholarship Challenge
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill Mob.: +91-9888096255 \\
\hspace*{0pt}\hfill Email: \textbf{\href{mailto:puneet29saini@gmail.com}{puneet29saini@gmail.com}} \\
\hspace*{0pt}\hfill Web: \textbf{\href{https://puneet29.github.io}{https://puneet29.github.io}} \\
\hspace*{0pt}\hfill \faicon{github} \href{https://github.com/puneet29}{\custombold{puneet29}} \faicon{linkedin} \href{https://www.linkedin.com/in/geekpuneet}{\custombold{geekpuneet}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2020-now} \runsubsection{TCS, Bengaluru}
\descript{Data Engineer}
\noindent
\hspace{2.8em}%
\begin{minipage}{0.85\textwidth\vspace{0pt}}
\begin{tightemize}
	\item \custombold{Developing data pipelines to create business reports:}
	\begin{subtightemize}
		\item Translate business propositions into quantitative queries and collect/clean the necessary data.
		\item Built scalable databases capable of ETL processes using SQL and Spark.
		\item Analysis of data to create dimension and fact tables.
		\item Created shell scripts to automate pipeline jobs.
	\end{subtightemize}
	\item \custombold{Automating the testing of recurring jobs:}
	\begin{subtightemize}
		\item Automated the testing process. Increased efficiency by 80\%.
		\item Created shell scripts to automate mailing list for daily\\
		reconciliation report.
	\end{subtightemize}
\end{tightemize}
\end{minipage}
\descriptright{Scala, Spark, Hadoop, Hive, Oracle SQL, Jira, Unix}
\sectionsep

\datecolor{2020-2020} \runsubsection{\href{https://www.stylumia.ai/}{Stylumia}}
\descript{Data Science Intern}
\noindent
\hspace{2.8em}%
\begin{minipage}{0.85\textwidth\vspace{0pt}}
\begin{tightemize}
	\item[] \companydescript{Leading ML startup in FashionAI domain}
	\item \custombold{Predicting future sales using market and client data:}
	\begin{subtightemize}
		\item Used time series forecasting based methods to predict the future period for time series data.
		\item Used classical machine learning and deep learning models to predict sales of new product.
	\end{subtightemize}
	\item \custombold{Creating a high level visualization library based on Plotly:}
	\begin{subtightemize}
		\item Developed a high level data visualization library to improve efficiency by 60\%.
		\item Developed a project to integrate graphs to dashboards easily, helping clients to explore their data.
	\end{subtightemize}
\end{tightemize}
\end{minipage}
\descriptright{Python, Pandas, Numpy, Scikit, Pytorch, Plotly, Jupyter, FBProphet, Flask}
\sectionsep

\datecolor{2018-2018} \runsubsection{Redinmex, Mexico - Remote}
\descript{Freelancer}
\noindent
\hspace{2.8em}%
\begin{minipage}{0.85\textwidth\vspace{0pt}}
\begin{tightemize}
	\item \custombold{Crime Detection in CCTV video:}
	\begin{subtightemize}
		\item Gathered appropriate data to train the C3D model on.
		\item Created visualization for anomaly detection for end user.
		\item Created custom dataloader for handling large dataset.
		\item Managing VMs in Azure and VastAI for loading and running model training.
	\end{subtightemize}
\end{tightemize}
\end{minipage}
\descriptright{Python, OpenCV, Jupyter, VastAI, Pytorch, Numpy, Pandas, Azure}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACADEMIC PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Projects}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{2020-now} \runsubsection{Tic Tac Toe RL}
\descript{Python, Numpy, Pygame}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Tic Tac Toe reinforcement learning model using Deep Q Learning.
Also included the minmax model to train Q learning model.
Made the GUI in Pygame.
\end{minipage}
\datecolor{2019-now} \runsubsection{Fast Artistic Style Transfer}
\descript{Pytorch, Flask, AWS S3, AWS EC2}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
A web app made using flask which uses pretrained models to stylize your image
with selected style image. Implemented using Johnson et al. paper.
\end{minipage}
\datecolor{2019-now} \runsubsection{Intel Scene Classification}
\descript{Pytorch, Jupyter, Flask}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Scene Classification model for Analytics Vidhya's Competition.\\
Hosted the app on Heroku.
\end{minipage}
\datecolor{2019-now} \runsubsection{Skin Cancer Classification}
\descript{Pytorch, Jupyter}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Skin cancer classification model which classifies three types of skin cancers.
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}